\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-25 paper.tex
evaluation-revision1

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Monetary loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall monetary gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{BA demands arrive with poisson process and their duration are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\begin{figure}
\centering
\subfigure[Link utilization]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/att.pdf}}
\subfigure[Admission time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/cernet3.pdf}}
\caption{Scalability of admission control.}
\label{admission-benefit}
\end{figure}

@@

%
%
%
%
%
%
%
% \begin{figure}[h]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/fake/totalprofit.pdf}
%\caption{Profit comparison between $\mathsf{BATE}$ and other Traffic engineering schemes.}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{BATE}$  rejects only about 3\% more demands than the optimal solution and can accept up to 50\% more demands than the \textit{Fixed} consistently.
Figure \ref{availability_fig1}(b) demonstrates  $\mathsf{BATE}$ is able to maintain at least 10\% higher link utilization than \textit{Fixed} algorithm.
We qualify the scalability by measuring the admission control time for each demand.
The simulation is performed on a Linux server (4-core, 2.60GHz processor with 32GB).
As shown in Figure \ref{admission-benefit}, the admission control time of $\mathsf{BATE}$ is less than 1s with about less than 5\% error, which is at least 30$\times$ faster the global optimal solution.

Similar to \cite{Teavar}, we next start a post-processing simulation, in which intends to send entirely bandwidth under each scenario at each time slot.
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{availability_fig1}(b) demonstrates that $\mathsf{BATE}$ can make 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{availability_fig1}(c) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
Figure \ref{availability_fig1}(d) shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{BATE}$  is able to retain 30\% more profit than other algorithms when network fails.
\begin{figure}
\centering
\subfigure[Cutoff error]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Optimization time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Impact of pruning for traffic scheduling.}
\label{availability_fig3}
\end{figure}
\begin{figure*} 
   \begin{minipage}[t]{0.24\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.24\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}
     \begin{minipage}[t]{0.24\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}
       \begin{minipage}[t]{0.24\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

\end{figure*}

Algorithm \ref{pruning} cuts off the scenarios that can hardly happen.
%Algorithm \ref{pruning} runs in depth-first manner and when the current network state is smaller than the threshold, the remaining state of the search tree can be ignored.
%Figure \ref{purning_fig2} (a) shows the percentage of network state coverage.
%We can see that even with small cutoff threshold, more than 97\% probability are included.
% In Section \ref{solutions}, we show how to derive the solutions for WAPM problem.
% The errors mainly comes from two parts, i.e., ILP approximate algorithm and pruning.
%In Appendix \ref{B}, we analyze the approximation of the greedy heuristic is 2 in an ideal case.
%Algorithm \ref{greedy} proposes a greedy algorithm to solve $\mathsf{BATE}$ problem.
Let $\mathsf{BATE}$ denote the overall achieved availability of all admitted demands with scenario pruning  and $OPT$ denote the achieved availability of optimal solution without scenario pruning. 
Then the error can be defined as $\frac{|\mathsf{BATE} -OPT|}{|OPT|}$.
Figure \ref{availability_fig3} (a) shows the error of pruning algorithm with different current link failure numbers.
We can see the error is less than 8\% even the current link failure number is 1.
Traditionally, TE should update the network state every 5-10 minutes.
% and though the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can solve $\mathsf{BATE}$ problem, it might be too slow.
Figure \ref{availability_fig3} (b) shows the time when solving it with Gurobi \cite{gurobi} on the server (4-core, 2.60GHz processor with 32GB ).
We can see that even on a large network (e.g., ATT topology), at most  15 seconds are needed when current link failure numbers are 2, which is fast enough in reality.
%We can see that for large network (e.g., ATT topology) , Gurobi is too slow to converge and the greedy algorithm is necessary.
%While the bruce force algorithm is more than 1000 minutes for each topology and we don't paint them in the picture.
%We can see the result is fast enough to deploy in practice.

>>>>

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Bandwidth availability]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Profit loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall profit gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{BA demands arrive with poisson process and their duration are with exponential distribution.}
\label{e2}
\end{figure*}

@@

\begin{figure}
\centering
\subfigure[No extra admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fixed-scheduling.pdf}}
\subfigure[Fixed admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/no-fixed.pdf}}
\caption{Traffic scheduling schemes comparisons.}
\label{scheduling-benefit}
\end{figure}

@@

%
%
%
%
%
%
%
 \begin{figure}[h]
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}

@@

%\includegraphics[width=0.24\textwidth]{fig/evaluation/sim-monney.pdf}}

@@

Figure \ref{availability_fig1}(a)  shows $\mathsf{BATE}$  rejects only about 3\% more demands than the optimal solution and can accept up to 50\% more demands than the \textit{Fixed} consistently.
Figure \ref{availability_fig1}(b) demonstrates  $\mathsf{BATE}$ is able to maintain at least 10\% higher link utilization than \textit{Fixed} algorithm.
We qualify the scalability by measuring the admission control time for each demand.
The simulation is performed on a Linux server (4-core, 2.60GHz processor with 32GB).
As shown in Figure \ref{availability_fig1}(c), the admission control time of $\mathsf{BATE}$ is less than 1s with about less than 5\% error, which is at least 30$\times$ faster the global optimal solution.

Similar to \cite{Teavar}, we next start a post-processing simulation, in which intends to send entirely bandwidth under each scenario at each time slot.
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.

Figure \ref{sim-profit} shows the average monetary gain percentage for the scenario in which one failure could occur in the network.
We can see $\mathsf{BATE}$  is able to retain 30\% more profit than other algorithms when network fails.

\begin{figure}
\centering
\subfigure[Cutoff error]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/error.pdf}}
\subfigure[Optimization time]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/optimization_time.pdf}}
\caption{Impact of pruning for traffic scheduling.}
\label{availability_fig3}
\end{figure}

% \begin{figure}
%\begin{center}
%\includegraphics [width=0.7\columnwidth] {fig/evaluation/routing.pdf}
%\caption{Different routing schemes comparison}
%\label{routing-version}
%\end{center}
%\end{figure}
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.7\columnwidth] {fig/evaluation/approximation.pdf}
%\caption{Approximation.}
%\label{approximation}
%\end{center}
%\end{figure}

\begin{figure} 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
    \caption{Routings.} 
    \label{routing-version} 
  \end{minipage}% 
   \begin{minipage}[t]{0.5\linewidth} 
    \centering 
    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
    \caption{Approximation.} 
    \label{approximation} 
  \end{minipage}

\end{figure}

%\begin{figure*} 
%   \begin{minipage}[t]{0.24\linewidth} 
%    \centering 
%    \includegraphics[width=1.6 in]{fig/evaluation/routing.pdf}
%    \caption{Routings.} 
%    \label{routing-version} 
%  \end{minipage}% 
%   \begin{minipage}[t]{0.24\linewidth} 
%    \centering 
%    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
%    \caption{Approximation.} 
%    \label{approximation} 
%  \end{minipage}
%     \begin{minipage}[t]{0.24\linewidth} 
%    \centering 
%    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
%    \caption{Approximation.} 
%    \label{approximation} 
%  \end{minipage}
%       \begin{minipage}[t]{0.24\linewidth} 
%    \centering 
%    \includegraphics[width=1.6 in]{fig/evaluation/approximation.pdf}
%    \caption{Approximation.} 
%    \label{approximation} 
%  \end{minipage}
%  
%\end{figure*}

Traffic scheduling algorithm cuts off the scenarios that can hardly happen.
%Algorithm \ref{pruning} runs in depth-first manner and when the current network state is smaller than the threshold, the remaining state of the search tree can be ignored.
%Figure \ref{purning_fig2} (a) shows the percentage of network state coverage.
%We can see that even with small cutoff threshold, more than 97\% probability are included.
% In Section \ref{solutions}, we show how to derive the solutions for WAPM problem.
% The errors mainly comes from two parts, i.e., ILP approximate algorithm and pruning.
%In Appendix \ref{B}, we analyze the approximation of the greedy heuristic is 2 in an ideal case.
%Algorithm \ref{greedy} proposes a greedy algorithm to solve $\mathsf{BATE}$ problem.
Let $\mathsf{BATE}$ denote the overall allocated bandwidth of all admitted demands with scenario pruning  and $OPT$ denote the allocated bandwidth of optimal solution without scenario pruning. 
Then the error can be defined as $\frac{|\mathsf{BATE} -OPT|}{|OPT|}$.
Figure \ref{availability_fig3} (a) shows the error of pruning algorithm with different current link failure numbers.
We can see the error is less than 8\% even the current link failure number is 1.
Traditionally, TE should update the network state every 5-10 minutes.
% and though the powerful mathematical optimization solver such as Gurobi \cite{gurobi} can solve $\mathsf{BATE}$ problem, it might be too slow.
Figure \ref{availability_fig3} (b) shows the time when solving it with Gurobi \cite{gurobi} on the server (4-core, 2.60GHz processor with 32GB ).
We can see that even on a large network (e.g., ATT topology), at most  15 seconds are needed when current link failure numbers are 2, which is fast enough in reality.
%We can see that for large network (e.g., ATT topology) , Gurobi is too slow to converge and the greedy algorithm is necessary.
%While the bruce force algorithm is more than 1000 minutes for each topology and we don't paint them in the picture.
%We can see the result is fast enough to deploy in practice.
